The limits of self commitment and private paternalism \thanks{}

### 2021-09-19 donde.tex
modification figure effect_contr_trakeup
Former-commit-id: de9c9ab193f7b524ead4995f4b70df412208be4b

\begin{figure}[H]
    \caption{Choice of contracts and treatment effects}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Chose wrong}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{By overconfidence/naivete}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_fee.pdf}

@@

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\% better when forced to fee-commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_fc_te_cf.pdf}

>>>>

\begin{figure}[H]
    \caption{Choice of contracts and treatment effects}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Chose wrong}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_eff_te_cf.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{By overconfidence/naivete}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_eff_te_cf_OC_fee.pdf}

@@

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\% better when forced to fee-commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_eff_te_cf.pdf}
